Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-29 programlogic.tex
+

Our reasoning principles are shaped around understanding the following main pillars of vritual-memory-management:

@@

\item page-table walk: L4-L1 walk on shared page tables to reach a physical page address
\item allocating/updating a pages backing a virtual address 

@@

>>>>

Our reasoning principles are shaped around understanding the following perspectives on the vritual-memory abstraction:

@@

\item a bag of physical pages reached through a set of physical page-table (L4-L1 page-tables) acceses which are shared amongst different virtual addresses indexed by the root address of the address-space 
\item allocating/updating pages backing a virtual address 

@@

With the reasoning principles introduced for the essential resource of address spaces, i.e. virtual memory addresses, now we can ...
